Untitled

### 2024-09-05 code/manuscript_analysis.Rmd
remove prelim stuff
making more figures

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

model <- did2s(
      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:2),]
```

@@

df.spill3 %>% 
   mutate(DistFilter = ifelse(Dist < quantile(Dist, 0.15), "Near", 
                              ifelse(Dist > quantile(Dist, 0.85), "Far", NA))) %>% 
  filter(!is.na(DistFilter) & Year == 2012) %>% 
  select(DistFilter, Tx:NumberofPatients, ALAND10:l.popdensity) %>% 
  inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
  select(DistFilter, TotalPop:Uninsured) %>% 
  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
         PctUninsured = Uninsured / Unins.denom * 100, 
         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
         PctBlack = Black / TotalPop * 100, 
         PctHispanic = Hispanic / TotalPop * 100) %>% 
    tbl_summary(by = DistFilter, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()

@@

@@

    df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
      mutate(Type = "Incumbent") %>% 
      rbind(df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.x" = "BHCMISID", "Year")) %>% mutate(Type = "Rival")) %>% 
        mutate(Quality = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
      mutate(quick_ratio = as.numeric(quick_ratio),
             Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities) %>% 
      mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
      select(Type, Quality, Total, Altman, Pct.NHA:Pct.COM) %>% 
          tbl_summary(by = Type, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()

>>>>

model <- did2s(
      data = df.spill3  %>% filter((Dist > quantile(Dist, 0.85) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

model <- did2s(
      data = df.spill3  %>% filter((Dist < quantile(Dist, 0.15) & Att > 0) | Att == 0 ) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)) %>% 
        #mutate(Tx = ifelse(Att - 1 == Year, 1, Tx)) %>% 
        mutate(Total.Hours = ifelse(Total.Hours > quantile(Total.Hours, 0.975, na.rm = TRUE), quantile(Total.Hours, 0.975, na.rm = TRUE), 
                                    ifelse(Total.Hours < quantile(Total.Hours, 0.025, na.rm = TRUE), quantile(Total.Hours, 0.025, na.rm = TRUE), Total.Hours))) , 
      yname = "Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

cbind(colnames(df.spill3)[10:19], TEs.strat.far %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`), TEs.strat.close%>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`, `Pr...t..`))[c(6:10, 1:5),]
```

@@

df.spill3 %>% 
   mutate(DistFilter = ifelse(Dist < quantile(Dist, 0.15), "Near", 
                              ifelse(Dist > quantile(Dist, 0.85), "Far", NA))) %>% 
  filter(!is.na(DistFilter) & Year < 2013) %>% 
  select(DistFilter, Tx:NumberofPatients, ALAND10:l.popdensity) %>% 
  inner_join(census, by = c("Zip" = "ZipCode", "Year" = "YEAR")) %>% 
  select(DistFilter, TotalPop:Uninsured) %>% 
  mutate(PctMedicaid = Medicaid / MCD.denom * 100, 
         PctUninsured = Uninsured / Unins.denom * 100, 
         PctPoverty = IncomeBelowPoverty / PovertyStatusDet * 100, 
         PctBlack = Black / TotalPop * 100, 
         PctHispanic = Hispanic / TotalPop * 100) %>% 
    tbl_summary(by = DistFilter, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()

@@

ggsave(filename = "AppendixFigures10.png", path = "/Users/markow/Dropbox/Writing/CHC Competitive Shocks/Figures", plot = p.rival.dist, width = 10, height = 6)
```

@@

    df.z.dist %>% 
      mutate(Year = Year - 1) %>% 
      left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
      mutate(Type = "Incumbent") %>% 
      rbind(df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.x" = "BHCMISID", "Year")) %>% mutate(Type = "Rival")) %>% 
        mutate(Quality = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
      mutate(quick_ratio = as.numeric(quick_ratio),
             Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
             logPatsPerStaff = log(Total / Staff)) %>% 
      mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
      select(Type, Quality, Total, Altman, logPatsPerStaff, Pct.NHA:Pct.COM) %>% 
          tbl_summary(by = Type, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), 
                digits = list(everything() ~ c(1)), 
                missing = "no") %>% 
  add_p(test = everything() ~ "t.test", pvalue_fun = function(x) style_pvalue(x, digits = 3))
